\documentclass[12pt]{article}
\usepackage{amsmath, amssymb}
\title{IMO 1961}
\date{}
\begin{document}
\maketitle

\textbf{Problem 1.}
Solve the system of equations:
\[
x + y + z = a, \quad x^2 + y^2 + z^2 = b^2, \quad xy = z^2,
\]
where $a$ and $b$ are constants. Give the conditions that $a$ and $b$ must satisfy so that $x, y, z$ (the solutions of the system) are distinct positive numbers.

\bigskip

\textbf{Problem 2.}
Let $a, b, c$ be the sides of a triangle, and $T$ its area. Prove:
\[
a^2 + b^2 + c^2 \geq 4\sqrt{3}\,T.
\]
In what case does equality hold?

\bigskip

\textbf{Problem 3.}
Solve the equation $\cos^n x - \sin^n x = 1$, where $n$ is a natural number.

\bigskip

\textbf{Problem 4.}
Consider triangle $P_1P_2P_3$ and a point $P$ within the triangle. Lines $P_1P$, $P_2P$, $P_3P$ intersect the opposite sides in points $Q_1$, $Q_2$, $Q_3$ respectively. Prove that, of the numbers
\[
\frac{P_1P}{PQ_1},\quad \frac{P_2P}{PQ_2},\quad \frac{P_3P}{PQ_3},
\]
at least one is $\leq 2$ and at least one is $\geq 2$.

\bigskip

\textbf{Problem 5.}
Construct triangle $ABC$ if $AC = b$, $AB = c$ and $\angle AMB = \omega$, where $M$ is the midpoint of segment $BC$ and $\omega < 90^\circ$. Prove that a solution exists if and only if
\[
b\tan\frac{\omega}{2} \leq c < b.
\]
In what case does the equality hold?

\bigskip

\textbf{Problem 6.}
Consider a plane $\varepsilon$ and three non-collinear points $A$, $B$, $C$ on the same side of $\varepsilon$; suppose the plane determined by these three points is not parallel to $\varepsilon$. In plane $\varepsilon$ take three arbitrary points $A'$, $B'$, $C'$. Let $L$, $M$, $N$ be the midpoints of segments $AA'$, $BB'$, $CC'$; let $G$ be the centroid of triangle $LMN$. (We will not consider positions of the points $A'$, $B'$, $C'$ such that the points $L$, $M$, $N$ do not form a triangle.) What is the locus of point $G$ as $A'$, $B'$, $C'$ range independently over the plane $\varepsilon$?

\end{document}
