\documentclass[12pt]{article}
\usepackage{amsmath, amssymb}
\title{IMO 1966}
\date{}
\begin{document}
\maketitle

\textbf{Problem 1.}
In a mathematical contest, three problems, $A$, $B$, $C$ were posed. Among the participants there were 25 students who solved at least one problem each. Of all the contestants who did not solve problem $A$, the number who solved $B$ was twice the number who solved $C$. The number of students who solved only problem $A$ was one more than the number of students who solved $A$ and at least one other problem. Of all students who solved just one problem, half did not solve problem $A$. How many students solved only problem $B$?

\bigskip

\textbf{Problem 2.}
Let $a, b, c$ be the lengths of the sides of a triangle, and $\alpha, \beta, \gamma$, respectively, the angles opposite these sides. Prove that if
\[
a + b = \tan\frac{\gamma}{2}(a\tan\alpha + b\tan\beta),
\]
the triangle is isosceles.

\bigskip

\textbf{Problem 3.}
Prove: The sum of the distances of the vertices of a regular tetrahedron from the center of its circumscribed sphere is less than the sum of the distances of these vertices from any other point in space.

\bigskip

\textbf{Problem 4.}
Prove that for every natural number $n$, and for every real number $x \neq k\pi/2^t$ ($t = 0, 1, \ldots, n$; $k$ any integer):
\[
\frac{1}{\sin 2x} + \frac{1}{\sin 4x} + \cdots + \frac{1}{\sin 2^n x} = \cot x - \cot 2^n x.
\]

\bigskip

\textbf{Problem 5.}
Solve the system of equations
\begin{align*}
|a_1 - a_2|\,x_2 + |a_1 - a_3|\,x_3 + |a_1 - a_4|\,x_4 &= 1,\\
|a_2 - a_1|\,x_1 + |a_2 - a_3|\,x_3 + |a_2 - a_4|\,x_4 &= 1,\\
|a_3 - a_1|\,x_1 + |a_3 - a_2|\,x_2 + |a_3 - a_4|\,x_4 &= 1,\\
|a_4 - a_1|\,x_1 + |a_4 - a_2|\,x_2 + |a_4 - a_3|\,x_3 &= 1,
\end{align*}
where $a_1, a_2, a_3, a_4$ are four different real numbers.

\bigskip

\textbf{Problem 6.}
In the interior of sides $BC$, $CA$, $AB$ of triangle $ABC$, any points $K$, $L$, $M$, respectively, are selected. Prove that the area of at least one of the triangles $AML$, $BKM$, $CLK$ is less than or equal to one quarter of the area of triangle $ABC$.

\end{document}
