\documentclass[12pt]{article}
\usepackage{amsmath, amssymb}
\title{IMO 1979}
\date{}
\begin{document}
\maketitle

\textbf{Problem 1.}
Let $p$ and $q$ be natural numbers such that
\[
\frac{p}{q} = 1 - \frac{1}{2} + \frac{1}{3} - \frac{1}{4} + \cdots - \frac{1}{1318} + \frac{1}{1319}.
\]
Prove that $p$ is divisible by $1979$.

\bigskip

\textbf{Problem 2.}
A prism with pentagons $A_1 A_2 A_3 A_4 A_5$ and $B_1 B_2 B_3 B_4 B_5$ as top and bottom faces is given. Each side of the two pentagons and each of the line-segments $A_i B_j$ for all $i, j = 1, \ldots, 5$, is colored either red or green. Every triangle whose vertices are vertices of the prism and whose sides have all been colored has two sides of a different color. Show that all $10$ sides of the top and bottom faces are the same color.

\bigskip

\textbf{Problem 3.}
Two circles in a plane intersect. Let $A$ be one of the points of intersection. Starting simultaneously from $A$ two points move with constant speeds, each point travelling along its own circle in the same sense. The two points return to $A$ simultaneously after one revolution. Prove that there is a fixed point $P$ in the plane such that, at any time, the distances from $P$ to the moving points are equal.

\bigskip

\textbf{Problem 4.}
Given a plane $\pi$, a point $P$ in this plane and a point $Q$ not in $\pi$, find all points $R$ in $\pi$ such that the ratio $(QP + PA)/QR$ is a maximum.

\bigskip

\textbf{Problem 5.}
Find all real numbers $a$ for which there exist non-negative real numbers $x_1, x_2, x_3, x_4, x_5$ satisfying the relations
\[
\sum_{k=1}^{5} k x_k = a, \quad \sum_{k=1}^{5} k^3 x_k = a^2, \quad \sum_{k=1}^{5} k^5 x_k = a^3.
\]

\bigskip

\textbf{Problem 6.}
Let $A$ and $E$ be opposite vertices of a regular octagon. A frog starts jumping at vertex $A$. From any vertex of the octagon except $E$, it may jump to either of the two adjacent vertices. When it reaches vertex $E$, the frog stops and stays there. Let $a_n$ be the number of distinct paths of exactly $n$ jumps ending at $E$. Prove that $a_{2n-1} = 0$,
\[
a_{2n} = \frac{1}{\sqrt{2}}(x^{n-1} - y^{n-1}), \quad n = 1, 2, 3, \ldots,
\]
where $x = 2 + \sqrt{2}$ and $y = 2 - \sqrt{2}$.

\medskip
\textit{Note.} A path of $n$ jumps is a sequence of vertices $(P_0, \ldots, P_n)$ such that
\begin{enumerate}
    \item[(i)] $P_0 = A$, $P_n = E$;
    \item[(ii)] for every $i$, $0 \leq i \leq n-1$, $P_i$ is distinct from $E$;
    \item[(iii)] for every $i$, $0 \leq i \leq n-1$, $P_i$ and $P_{i+1}$ are adjacent.
\end{enumerate}

\end{document}
