\documentclass[12pt]{article}
\usepackage{amsmath, amssymb}
\title{IMO 1990}
\date{}
\begin{document}
\maketitle

\textbf{Problem 1.}
Chords $AB$ and $CD$ of a circle intersect at a point $E$ inside the circle. Let $M$ be an interior point of the segment $EB$. The tangent line at $E$ to the circle through $D$, $E$, and $M$ intersects the lines $BC$ and $AC$ at $F$ and $G$, respectively. If
\[
\frac{AM}{AB} = t,
\]
find $\dfrac{EG}{EF}$ in terms of $t$.

\bigskip

\textbf{Problem 2.}
Let $n \geq 3$ and consider a set $E$ of $2n - 1$ distinct points on a circle. Suppose that exactly $k$ of these points are to be colored black. Such a coloring is ``good'' if there is at least one pair of black points such that the interior of one of the arcs between them contains exactly $n$ points from $E$. Find the smallest value of $k$ so that every such coloring of $k$ points of $E$ is good.

\bigskip

\textbf{Problem 3.}
Determine all integers $n > 1$ such that
\[
\frac{2^n + 1}{n^2}
\]
is an integer.

\bigskip

\textbf{Problem 4.}
Let $\mathbb{Q}^+$ be the set of positive rational numbers. Construct a function $f : \mathbb{Q}^+ \to \mathbb{Q}^+$ such that
\[
f(xf(y)) = \frac{f(x)}{y}
\]
for all $x, y$ in $\mathbb{Q}^+$.

\bigskip

\textbf{Problem 5.}
Given an initial integer $n_0 > 1$, two players, $A$ and $B$, choose integers $n_1, n_2, n_3, \ldots$ alternately according to the following rules:

Knowing $n_{2k}$, $A$ chooses any integer $n_{2k+1}$ such that
\[
n_{2k} \leq n_{2k+1} \leq n_{2k}^2.
\]
Knowing $n_{2k+1}$, $B$ chooses any integer $n_{2k+2}$ such that
\[
\frac{n_{2k+1}}{n_{2k+2}}
\]
is a prime raised to a positive integer power.

Player $A$ wins the game by choosing the number $1990$; player $B$ wins by choosing the number $1$. For which $n_0$ does:
\begin{enumerate}
\item[(a)] $A$ have a winning strategy?
\item[(b)] $B$ have a winning strategy?
\item[(c)] Neither player have a winning strategy?
\end{enumerate}

\bigskip

\textbf{Problem 6.}
Prove that there exists a convex $1990$-gon with the following two properties:
\begin{enumerate}
\item[(a)] All angles are equal.
\item[(b)] The lengths of the $1990$ sides are the numbers $1^2, 2^2, 3^2, \ldots, 1990^2$ in some order.
\end{enumerate}

\end{document}
