\documentclass[12pt]{article}
\usepackage{amsmath, amssymb}
\title{IMO 1993}
\date{}
\begin{document}
\maketitle

\textbf{Problem 1.}
Let $f(x) = x^n + 5x^{n-1} + 3$, where $n > 1$ is an integer. Prove that $f(x)$ cannot be expressed as the product of two nonconstant polynomials with integer coefficients.

\bigskip

\textbf{Problem 2.}
Let $D$ be a point inside acute triangle $ABC$ such that $\angle ADB = \angle ACB + \pi/2$ and $AC \cdot BD = AD \cdot BC$.
\begin{enumerate}
\item[(a)] Calculate the ratio $(AB \cdot CD)/(AC \cdot BD)$.
\item[(b)] Prove that the tangents at $C$ to the circumcircles of $\triangle ACD$ and $\triangle BCD$ are perpendicular.
\end{enumerate}

\bigskip

\textbf{Problem 3.}
On an infinite chessboard, a game is played as follows. At the start, $n^2$ pieces are arranged on the chessboard in an $n \times n$ block of adjoining squares, one piece in each square. A move in the game is a jump in a horizontal or vertical direction over an adjacent occupied square to an unoccupied square immediately beyond. The piece which has been jumped over is removed.

Find those values of $n$ for which the game can end with only one piece remaining on the board.

\bigskip

\textbf{Problem 4.}
For three points $P, Q, R$ in the plane, we define $m(PQR)$ as the minimum length of the three altitudes of $\triangle PQR$. (If the points are collinear, we set $m(PQR) = 0$.)

Prove that for points $A, B, C, X$ in the plane,
\[
m(ABC) \leq m(ABX) + m(AXC) + m(XBC).
\]

\bigskip

\textbf{Problem 5.}
Does there exist a function $f : \mathbb{N} \to \mathbb{N}$ such that $f(1) = 2$, $f(f(n)) = f(n) + n$ for all $n \in \mathbb{N}$, and $f(n) < f(n+1)$ for all $n \in \mathbb{N}$?

\bigskip

\textbf{Problem 6.}
There are $n$ lamps $L_0, \ldots, L_{n-1}$ in a circle ($n > 1$), where we denote $L_{n+k} = L_k$. (A lamp at all times is either on or off.) Perform steps $s_0, s_1, \ldots$ as follows: at step $s_i$, if $L_{i-1}$ is lit, switch $L_i$ from on to off or vice versa, otherwise do nothing. Initially all lamps are on. Show that:
\begin{enumerate}
\item[(a)] There is a positive integer $M(n)$ such that after $M(n)$ steps all the lamps are on again;
\item[(b)] If $n = 2^k$, we can take $M(n) = n^2 - 1$;
\item[(c)] If $n = 2^k + 1$, we can take $M(n) = n^2 - n + 1$.
\end{enumerate}

\end{document}
