\documentclass[12pt]{article}
\usepackage{amsmath, amssymb}
\title{IMO 1998}
\date{}
\begin{document}
\maketitle

\textbf{Problem 1.}
In the convex quadrilateral $ABCD$, the diagonals $AC$ and $BD$ are perpendicular and the opposite sides $AB$ and $DC$ are not parallel. Suppose that the point $P$, where the perpendicular bisectors of $AB$ and $DC$ meet, is inside $ABCD$. Prove that $ABCD$ is a cyclic quadrilateral if and only if the triangles $ABP$ and $CDP$ have equal areas.

\bigskip

\textbf{Problem 2.}
In a competition, there are $a$ contestants and $b$ judges, where $b \geq 3$ is an odd integer. Each judge rates each contestant as either ``pass'' or ``fail''. Suppose $k$ is a number such that, for any two judges, their ratings coincide for at most $k$ contestants. Prove that
\[
\frac{k}{a} \geq \frac{b-1}{2b}.
\]

\bigskip

\textbf{Problem 3.}
For any positive integer $n$, let $d(n)$ denote the number of positive divisors of $n$ (including $1$ and $n$ itself). Determine all positive integers $k$ such that
\[
\frac{d(n^2)}{d(n)} = k
\]
for some $n$.

\bigskip

\textbf{Problem 4.}
Determine all pairs $(a, b)$ of positive integers such that $ab^2 + b + 7$ divides $a^2b + a + b$.

\bigskip

\textbf{Problem 5.}
Let $I$ be the incenter of triangle $ABC$. Let the incircle of $ABC$ touch the sides $BC$, $CA$, and $AB$ at $K$, $L$, and $M$, respectively. The line through $B$ parallel to $MK$ meets the lines $LM$ and $LK$ at $R$ and $S$, respectively. Prove that $\angle RIS$ is acute.

\bigskip

\textbf{Problem 6.}
Consider all functions $f$ from the set $\mathbb{N}$ of all positive integers into itself satisfying
\[
f(t^2 f(s)) = s(f(t))^2
\]
for all $s$ and $t$ in $\mathbb{N}$. Determine the least possible value of $f(1998)$.

\end{document}
